\documentclass{article}

\usepackage[margin=0.75in]{geometry}

\title{Bylaws}
\author{Miami University Student Chapter of the Association for Computing Machinery}
\date{Revised 2016-07-27}

\renewcommand{\thesection}{Article \Roman{section}:}
\renewcommand{\theenumi}{\Alph{enumi}}

\begin{document}
\maketitle

\section{Name}
This organization shall be called the Miami University Student Chapter of the
Association for Computing Machinery.

\section{Purpose}
The Chapter is organized and will be operated exclusively for educational,
scientific, and social purposes and in furtherance thereof.

\begin{enumerate}
	\item to promote an increased knowledge of the science, design, development,
		construction, languages, and applications of modern computing machinery.

	\item To promote a greater interest in computing machinery and its applications.

	\item To provide a means of communication between persons having interest in
		computing machinery.

	\item To assist the community and provide it with a better understanding in
		relation to computing machinery and its applications.
\end{enumerate}

\section{Membership}
\begin{enumerate}
	\item Membership shall be open to all Student Members of the ACM who are members
		of the Miami University community.

	\item Affiliate membership in this chapter shall be open to all non-ACM
		members who are students at Miami University. Affiliate members'
		activity is limited to local affairs.

	\item Regular participation in Chapter activities is expected by all members. A
		member who fails to attend at least half of the regular on-campus Chapter
		meetings per semester will be considered inactive and may be removed from
		Chapter membership by the Secretary.

	\item All Miami University students and faculty that wish to become members
		must join the Miami University Chapter of the Association for Computing
		Machinery on The HUB.
\end{enumerate}

\section{Officers}
\begin{enumerate}
	\item The officers of this chapter shall be the President, Vice-President,
		Secretary, Treasurer, and Membership Chair. They all must become
		student members of ACM and of this Chapter.

	\item The officers shall be elected at the annual election meeting to be
		held during the last meeting in April or at the meeting nearest to the
		last week in April. Nominations shall be taken at the meeting prior to
		the annual election meeting and by submission of nominations in writing
		to the current officers or faculty advisor.

	\item Each active member of this chapter is entitled to nominate no more
		than one member for each officer position, including themselves. Each
		nomination must be accepted by the nominated member and seconded by
		a member other than the nominating member or the nominated member.

	\item The cut-off date for submission of nominations shall be established by
		the current officers.  Any Chapter member who anticipates that he/she
		will attend Miami for the following complete academic year is eligible
		for office.

\end{enumerate}

\end{document}
